Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-01-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Reducing a bit names using acronyms refs #84

\author{Juan-J.~Merelo, Dept. of Computer Architecture and Technology, University of Granada, Granada, Spain\\Mario Garc\'ia-Valdez, Dept. of Graduate Studies, Instituto Tecnológico de Tijuana, Tijuana, M\'exico\\Pedro A. Castillo, Dept. of Computer Architecture and Technology, University of Granada, Granada, Spain\\Pablo Garc\'ia-S\'anchez, Dept. of Computer Architecture and Technology, University of Granada, Granada, Spain\\Paloma de las Cuevas, Dept. of Computer Architecture and Technology, University of Granada, Granada, Spain\\Nuria Rico, Dept. of Statistics and Operational Research, University of Granada, Granada, Spain%

>>>>

\author{Juan-J.~Merelo, Dept. of Computer Architecture and Technology
  (CAT), University of Granada, Granada, Spain (UGR)\\
Mario Garc\'ia-Valdez, Dept. of Graduate Studies, Instituto
Tecnológico de Tijuana, Tijuana, M\'exico\\
Pedro A. Castillo, Dept. of CAT, UGR\\
Pablo Garc\'ia-S\'anchez, Dept. of CAT, UGR\\
Paloma de las Cuevas, Dept. of CAT, UGR\\Nuria Rico, Dept. of Statistics and Operational Research, UGR%
